---
title: "The analysis of NHS"
subtitle: ""
author: "Franklin Fang"
date: "Last updated 24th December 2020"
output:
  flexdashboard::flex_dashboard:
  runtime: flexdashboard  
  html_document:
    theme: "journal"  
---

## Coversheet

  Title: ...
  CASA0005 Geographic Information Systems and Science
  The Bartlett Centre for Advanced Spatial Analysis
  Github repository URL: https://github.com/Hereislittlemushroom/CASA0005_Final_Assessment
  Online website RPubs: https://zeqiang.fun/

## Instruction

we can actually set up a topic such as 

## Research Question

## Literature Review

## Methodology

### Data Source

### Data Limitation

tip: you can use the APOCA method (authority/purpose/objectivity/currency/accuracy)

## Results

### Descriptive statistics

### Further analysis

## Discussion

### Recommendations

## Conclusion

## References

## Reproducible analysis

### Read data into R

And then, I need a map of London borough
```{r}
library(sf)
London_Borough = st_read("/Users/fangzeqiang/Desktop/SDSV/Final/CASA0005_Final_Assessment/Dataset/statistical-gis-boundaries-london/ESRI/London_Borough_Excluding_MHW.shp")
# .shp should be loaded in ESRI folder and path instead of relative path!
plot(st_geometry(London_Borough))
```
The NCR is a database of publicly-available chargepoints for electric vehicles in the UK established in 2011(,2021).

you can access data in this
[link](https://www.gov.uk/guidance/find-and-use-data-on-public-electric-vehicle-chargepoints#accessing-data-on-ncv)
```{r}
library(tidyverse)
charge_points = read_csv("Dataset/national-charge-point-registry.csv")
summary(charge_points)
```
```{r}
charge_points
```

### Data preprocessing

### Analysis

- weighted 
- 

### 